Relevance-based Quantization of Scattering Features for Unsupervised Mining of Environmental Audio

### 2018-02-03 paper/structureScene.tex
Edit results section

This section presents evaluation results for the acoustic scene similarity retrieval task. The $p@k$ for different settings are shown in Figure \ref{fig:ASS_1}, illustrating the effect of the different similarity metrics. The metrics is shown for values of $k$ up to 9 which corresponds to the number of elements minus one within each class of scene of the dataset. This allows us to also evaluate the recall capabilities of the system under evaluation.

@@

For the scattering transform, both \emph{RbQ-c} and \emph{RbQ-w} outperform \emph{early}, thus confirming the benefits of using an relevance-based quantization (RbQ) to improve the similarity measures between the scenes. However, it is worth noticing that \emph{RbQ-a} performs worse or comparably to \emph{early}, showing that the discriminant information is destroyed by averaging the contributions from all centroids. This result is in line with the findings of \cite{lagrange:hal-01082501}. To take advantage of an such a representation, we need to select certain representative centroids when comparing quantized objects. Furthermore, it appears that \emph{RbQ-c} is better able to characterize the classes than \emph{RbQ-w}. This last observation suggests that weighting a centroid according to the number of frames it contains may prove to be a limited solution. Indeed, nothing a priori indicates that the discriminant information between two scenes lays within the majority of their frames. On the contrary, two similar environments may shared a lot of similar sound sources with only a few sources discriminating between them.

Considering the $p@5$ as in \cite{aucouturier2007bag} and \cite{lagrange:hal-01082501} as our metric, the use of the log-scattering transform versus MFCCs increases the performance  from 0.31 to 0.49 and the use of the relevance based quantization approach using the closest similarity (RbQ-c) further improves the performance to 0.54 for a global increase of 0.23.

>>>>

This section presents evaluation results for the acoustic scene similarity retrieval task. The $p@k$ for different settings are shown in Figure \ref{fig:ASS_1}, illustrating the effect of the different similarity metrics. This allows us to also evaluate the recall capabilities of the system under evaluation.

@@

For the scattering transform, both \emph{RbQ-c} and \emph{RbQ-w} outperform \emph{early}, thus confirming the benefits of using an relevance-based quantization (\emph{RbQ}) to improve the similarity measures between the scenes. However, it is worth noticing that \emph{RbQ-a} performs worse or comparably to \emph{early}, showing that the discriminant information is destroyed by averaging the contributions from all centroids. This result is in line with the findings of \cite{lagrange:hal-01082501}. To take advantage of such a representation, we need to select certain representative centroids when comparing quantized objects. Furthermore, it appears that \emph{RbQ-c} is better able to characterize the classes compared to \emph{RbQ-w}. This last observation suggests that weighting a centroid according to the number of frames it contains may prove to be a limited solution. Indeed, nothing a priori indicates that the discriminant information between two scenes lays within the majority of their frames. On the contrary, two similar environments may share a lot of similar sound sources with only a few sources discriminating between them. \ml{This is a bit of a stretch, since it may just be that we used the wrong distance to take the weighting into account. Perhaps the non-normalize d EMD is not appropriate here?}

Considering $p@5$ as our metric (as in \cite{aucouturier2007bag} and \cite{lagrange:hal-01082501}), the use of the log-scattering transform instead of MFCCs increases the performance from $0.31$ to $0.49$ and the use of the relevance-based quantization approach using the closest similarity (\emph{RbQ-c}) further improves the performance to $0.54$ for a global increase of $0.23$.
